### 2021-06-15 papers/thesis/full/ch4-spherical-caps/spherical-caps.tex
Minor edits to preamble and help with spacing issues for large eqn environments

By construction, $\{\scopnkia\}$ are orthogonal with respect to the inner product \nomenclature[innerQ]{$\ip< p, \: q >_{\scopa}$}{A multidimensional inner product over $\Omega$ with the weight $\Wa$ associated with the OPs $\{\scopnkia\}$}
\bseqn{
	\ip< p, \: q >_{\scopa} &:= \int_\Omega p(\xvec, z) \: q(\xvec, z) \: \genjacw^{(a,0)}(z) \: \D A \\
	&= \int_\alpha^1 \int_0^{2\pi} p(\rho(z) \cos\theta, \rho(z) \sin\theta, z) \: q(\rho(z) \cos\theta, \rho(z) \sin\theta, z) \: \D \theta \: \genjacw^{(a,0)}(z) \: \D z,
}
with \nomenclature[normQ]{$\norm{f}_{\scopa}$}{The norm of a function f, defined by the square root of the inner product over $\Omega$ given by the weight $\Wa$ associated with the OPs $\{\scopnkia\}$}
\bseqnnumber{
	\norm{\scopnkia}_{\scopa}^2 &:= \ip< \scopnkia, \: \scopnkia >_{\scopa} = \pi \: \normgenjac^{(a, 2k)}. \label{eqn:sc:normscop}
}
A method for obtaining explicit recurrence coefficients and evaluating integrals for the weight function $\genjacw^{(a,b)}(x)$ was established in \bsrefchapter{CHAPTER:diskslice} (see also \cite{snowball2019sparse}). The weight is in fact semi-classical, and is equivalent to a generalized Jacobi weight \cite[\S5]{magnus1995painleve}.

@@

\begin{lemma}\label{lemma:sc:Qrecurrence} 
Define
\bseqnnumber{
	\eta_{k} :=
		\begin{cases}
			0 &\text{if } k < 0 \\
			\ch_0 &\text{if } k = 0 \\
			\half &\text{otherwise}
		\end{cases}
}
$\scopnkia(x,y,z)$ satisfy the following recurrences:
\bseqn{
	x \: \scopnkia(x,y,z) &= \alphaa_{n,k,1} \:  \scopa_{n-1, k-1, i}(x, y, z) + \alphaa_{n,k,2} \:  \scopa_{n-1, k+1, i}(x, y, z) \nonumber \\
		& \quad + \alphaa_{n,k,3} \:  \scopa_{n, k-1, i}(x, y, z) + \alphaa_{n,k,4} \:  \scopa_{n, k+1, i}(x, y, z) \nonumber \\
		& \quad + \alphaa_{n,k,5} \:  \scopa_{n+1, k-1, i}(x, y, z) + \alphaa_{n,k,6} \:  \scopa_{n+1, k+1, i}(x, y, z), \\ \\
	y \: \scopnkia(x,y,z) &= \betaa_{n,k,i,1} \:  \scopa_{n-1, k-1, |i-1|}(x, y, z) + \betaa_{n,k,i,2} \:  \scopa_{n-1, k+1, |i-1|}(x, y, z) \nonumber \\
		& \quad + \betaa_{n,k,i,3} \:  \scopa_{n, k-1, |i-1|}(x, y, z) + \betaa_{n,k,i,4} \:  \scopa_{n, k+1, |i-1|}(x, y, z) \nonumber \\
		& \quad + \betaa_{n,k,i,5} \:  \scopa_{n+1, k-1, |i-1|}(x, y, z) + \betaa_{n,k,i,6} \:  \scopa_{n+1, k+1, |i-1|}(x, y, z), \\ \\
	z \: \scopnkia(x,y,z) &= \gammaa_{n,k,1} \: \scopa_{n-1, k, i}(x, y, z) + \gammaa_{n,k,2} \: \scopa_{n, k, i}(x, y, z) \nonumber \\
		& \quad + \gammaa_{n,k,3} \: \scopa_{n+1, k, i}(x, y, z),
}
for $(x,y,z) \in \Omega$, where
\bseqn{
	\alphaa_{n,k,1} &:= \eta_{k-1} \: \ip<\genjacnmk^{(a, 2k)}, \: \genjacnmk^{(a, 2(k-1))}>_{\genjacw^{(a, 2k)}}, \\
	\alphaa_{n,k,2} &:= \eta_{k} \: \ip<\genjacnmk^{(a, 2k)}, \genjac_{n-k-2}^{(a, 2(k+1))}>_{\genjacw^{(a, 2(k+1))}}, \\
	\alphaa_{n,k,3} &:=\eta_{k-1} \: \ip<\genjacnmk^{(a, 2k)}, \: \genjac_{n-k+1}^{(a, 2(k-1))}>_{\genjacw^{(a, 2k)}}, \\
	\alphaa_{n,k,4} &:= \eta_{k} \: \ip<\genjacnmk^{(a, 2k)}, \genjac_{n-k-1}^{(a, 2(k+1))}>_{\genjacw^{(a, 2(k+1))}}, \\
	\alphaa_{n,k,5} &:= \eta_{k-1} \: \ip<\genjacnmk^{(a, 2k)}, \: \genjac_{n-k+2}^{(a, 2(k-1))}>_{\genjacw^{(a, 2k)}}, \\
	\alphaa_{n,k,6} &:=\eta_{k} \: \ip<\genjacnmk^{(a, 2k)}, \genjacnmk^{(a, 2(k+1))}>_{\genjacw^{(a, 2(k+1))}}, \\
	\betaa_{n,k,i,j} &:= 
		\begin{cases}
			- \alphaa_{n,k,j} \quad &\text{if }(i = 0 \text{ and } j \text{ is odd}) \text{ or }(i = 1 \text{ and } j \text{ is even}) \\
			\alphaa_{n,k,j} \quad &\text{otherwise}
		\end{cases}, \\	
	\gammaa_{n,k,1} &:= \beta_{n-k-1}^{(a, 2k)}, \qquad \gammaa_{n,k,2} := \alpha_{n-k}^{(a, 2k)}, \qquad \gammaa_{n,k,3} := \beta_{n-k}^{(a, 2k)}.
}
\end{lemma}

@@

\begin{proof}
	The 3-term recurrence for multiplication by $z$ follows from \bsrefeqn{eqn:sc:Rrecurrence}. For the recurrence for multiplication by $x$, since $\{\scopmjha\}$ for $m = 0,\dots,n+1$, $j = 0,\dots,m$, $h = 0,1$ is an orthogonal basis for any degree $n+1$ polynomial on $\Omega$, we can expand 
\bseqn{
	x \: \scopnkia(x,y,z) = \sum_{m=0}^{n+1} \sum_{j=0}^m \sum_{h=0}^1 c_{m,j} \: \scopmjha(x,y,z).
}
These coefficients are given by
\bseqn{
	c_{m,j} = {\ip< x \: \scopnkia, \scopmjha >_{\scopa}}{\norm{\scopmjha}^{-2}_{\scopa}}
}
where we show the non-zero coefficients that result are the $\alphaa_{n,k,1},\dots,\alphaa_{n,k,6}$ in the lemma.
Recall from \bsrefeqn{eqn:sc:normscop} that $\norm{\scopmjha}_{\scopa}^2 = \pi \: \normgenjac^{(a,2j)}$. Using a change of variables 
\bseqn{
	(\cos\theta \sin\varphi, \: \sin\theta\sin\varphi, \: \cos\varphi) = (x, y, z)
}
we have that, for $m = 0,\dots,n+1$, $j = 0,\dots,m$, 
\bseqn{
	&\ip<x \: \scopnkia, \scopmjha>_{\scopa} \\
	&= \int_\Omega \scopnkia(\xvec,z) \: \scopmjha(\xvec,z) \: x \: \genjacw^{(a,0)}(z) \: \D A \\
	&= \Big( \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \rho(z)^{k+j+1} \: \genjacw^{(a, 0)}(z) \: \D z \Big) \\
	&\quadfour \cdot \Big( \int_0^{2\pi} \chki(\theta) \: \chjh(\theta) \: \cos\theta \: \D \theta \Big) \\
	&= \Big( \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \genjacw^{(a, k + j + 1)}(z) \: \D z \Big) \cdot \: \Big( \int_0^{2\pi} \chki(\theta) \: \chjh(\theta) \: \cos\theta \: \D \theta \Big) \\
	&= \half \: \pi \: \delta_{i,h} \: (\eta_{k-1} \: \delta_{k-1, j} + \eta_{k} \: \delta_{k+1, j})  \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \genjacw^{(a, k + j + 1)}(z) \: \D z
}
where $\delta_{k, j}$ is the standard Kronecker delta function, using \bsreflemma{lemma:sc:Yrecurrence}. Similarly, for the recurrence for multiplication by $y$, we can expand 
\bseqn{
	y \: \scopnkia(x,y,z) = \sum_{m=0}^{n+1} \sum_{j=0}^m \sum_{h=0}^1 d_{m,j} \: \scopmjha(x,y,z).
}
These coefficients are given by
\bseqn{
	d_{m,j} = {\ip< y \: \scopnkia, \scopmjha >_{\scopa}}{\norm{\scopmjha}^{-2}_{\scopa}}
}
where we show the non-zero coefficients that result are the $\betaa_{n,k,1},\dots,\betaa_{n,k,6}$ in the lemma:sc:
\bseqn{
	&\ip<y \: \scopnkia, \scopmjha>_{\scopa} \\
	&= \int_\Omega \scopnkia(\xvec,z) \: \scopmjha(\xvec,z) \: y \: \genjacw^{(a,0)}(z) \: \D A \\
	&= \Big( \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \rho(z)^{k+j+1} \: \genjacw^{(a, 0)}(z) \: \D z \Big) \\
	&\quadfour \cdot \Big( \int_0^{2\pi} \chki(\theta) \: \chjh(\theta) \: \sin\theta \: \D \theta \Big) \\
	&= \Big( \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \genjacw^{(a, k + j + 1)}(z) \: \D z \Big) \cdot \: \Big( \int_0^{2\pi} \chki(\theta) \: \chjh(\theta) \: \sin\theta \: \D \theta \Big) \\
	&= \half \: \pi \: \delta_{|i-1|,h} \: \big[(-1)^{i+1} \: \eta_{k-1} \: \delta_{k-1, j} + (-1)^i \: \eta_{k} \: \delta_{k+1, j}\big] \\
	&\quadfour \cdot \Big( \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \genjacw^{(a, k + j + 1)}(z) \: \D z \Big)
}
where again $\delta_{k, j}$ is the standard Kronecker delta function, and we have used \bsreflemma{lemma:sc:Yrecurrence}.

@@

For the operator $\calL_W^{(a)\to(a-\tilde a)}$ for the surface Laplacian on a weighted space, the entries of the operator are given by the coefficients in the expansion 
\bseqn{
	\DeltaS \big(\genjacw^{(a,0)} \: \scopnki^{(a)} \big) = \sum_{m=0}^{n} \sum_{j=0}^m \sum_{h=0}^1 c_{m,j,h} \: \genjacw^{(a-\tilde a,0)} \: \scopmjh^{(a - \tilde a)}, 
}	
where the coefficients are
\bseqn{
	c_{m,j,h} = \norm{\scopmjh^{(a - \tilde a)}}^{-2}_{\scop^{(a - \tilde a)}} \ip<\DeltaS \big(\genjacw^{(a,0)} \: \scopnki^{(a)} \big), \: \scopmjh^{(a - \tilde a)}>_{\scop^{(0)}}.
}
Using \bsrefeqn{eqn:sc:woplaplacian}, and integrating by parts thrice, we then have that
\bseqn{
	&\ip<\DeltaS \big(\genjacw^{(a,0)} \: \scopnki^{(a)} \big), \: \scopmjh^{(a - \tilde a)}>_{\scop^{(0)}} \\
	&= \Big( \int_0^{2\pi} \: \chki(\theta) \: \chjh(\theta) \: \D \theta \Big) \\
	&\quadfour \cdot \: \Big( \int_\alpha^1 \Big\{\genjacnmk^{(a,2k)} [-k(k+1) \genjacw^{(2,0)} - 2a(k+1)z \: \genjacw^{(1,0)} + a (a-1) \rho^2] \\
	&\quadeight + \genjacnmk^{(a,2k) \: \prime} [-2(k+1) z \: \genjacw^{(2,0)} + 2a \genjacw^{(1,2)}] \\
	&\quadeight + \genjacnmk^{(a,2k) \: \prime \prime} \: \genjacw^{(2,2)} \Big\} \: \genjacmmj^{(a - \tilde a, 2j)} \: \genjacw^{(a - 2, k+j)} \:  \D z \Big) \\
	&= \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \Big\{ \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacnmk^{(a,2k)} \: \genjacw^{(a - 2, 2k)} \: \big[ -k(k+1) \genjacw^{(2,0)} - 2a(k+1)z \: \genjacw^{(1,0)} \\
	&\quadeight \quadeight \quadtwo \quad + a (a-1) \rho^2 \big] \\
	&\quadeight + a \: \genjacnmk^{(a,2k) \: \prime} \: \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacw^{(a - 1, 2k+2)} \\
	&\quadeight + \genjac_{m-k}^{(a - \tilde a, 2k)} \: \ddx{z} [\genjacnmk^{(a,2k) \: \prime} \: \genjacw^{(a, 2k+2)}] \Big\} \: \D z \\
	&= \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \Big\{ \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacnmk^{(a,2k)} \: \genjacw^{(a - 2, 2k)} \: \big[ -k(k+1) \genjacw^{(2,0)} - 2a(k+1)z \: \genjacw^{(1,0)} \\
	&\quadeight \quadeight \quadtwo \quad + a (a-1) \rho^2 \big] \\
	&\quadeight + a \: \genjacnmk^{(a,2k) \: \prime} \: \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacw^{(a - 1, 2k+2)} \\
	&\quadeight + \genjacnmk^{(a,2k)} \: \genjacw^{(a-1, 2k)} \big[ \genjac_{m-k}^{(a - \tilde a, 2k) \: \prime \prime} \: \genjacw^{(1, 2)} + a \genjac_{m-k}^{(a - \tilde a, 2k) \: \prime} \: \rho^2 \\
	&\quadeight \quadeight \quadtwo \quad - 2(k+1) z \: \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacw^{(1, 0)} \big] \Big\} \: \D z \\
	&= \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \Big\{ \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacnmk^{(a,2k)} \: \genjacw^{(a - 2, 2k)} \: \big[ -k(k+1) \genjacw^{(2,0)} - 2a(k+1)z \: \genjacw^{(1,0)} \\
	&\quadeight \quadeight \quadtwo \quad + a (a-1) \rho^2 \big] \\
	&\quadfour \quadtwo + \genjacnmk^{(a,2k)} \: \genjacw^{(a - 1, 2k+2)} \big[ \genjac_{m-k}^{(a - \tilde a, 2k) \: \prime \prime} \: \rho^2 - 2(k+1) z \: \genjac_{m-k}^{(a - \tilde a, 2k) \: \prime} \big] \\
	&\quadfour \quadtwo - a \genjacnmk^{(a,2k)} \: \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacw^{(a-2, 2k)} \: \big[ (a-1) \rho^2 - 2(k+1) z \: \genjacw^{(1, 0)} \big] \Big\} \: \D z \\
	&= \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \genjacnmk^{(a,2k)} \: \genjacw^{(a, 2k)} \: r_{m-k} \: \D z
}
where $r_{m-k}$ is a degree $m - k$ polynomial in $z$, and so the above is zero for $n - k > m - k \iff m < n$.

>>>>

By construction, $\{\scopnkia\}$ are orthogonal with respect to the inner product \nomenclature[innerQ]{$\ip< p, \: q >_{\scopa}$}{A multidimensional inner product over $\Omega$ with the weight $\Wa$ associated with the OPs $\{\scopnkia\}$}
\bseqn{
	&\ip< p, \: q >_{\scopa} \\
	&:= \int_\Omega p(\xvec, z) \: q(\xvec, z) \: \genjacw^{(a,0)}(z) \: \D A \\
	&= \int_\alpha^1 \int_0^{2\pi} p(\rho(z) \cos\theta, \rho(z) \sin\theta, z) \: q(\rho(z) \cos\theta, \rho(z) \sin\theta, z) \: \D \theta \: \genjacw^{(a,0)}(z) \: \D z,
}
with \nomenclature[normQ]{$\norm{f}_{\scopa}$}{The norm of a function f, defined by the square root of the inner product over $\Omega$ given by the weight $\Wa$ associated with the OPs $\{\scopnkia\}$}
\bseqnnumber{
	\norm{\scopnkia}_{\scopa}^2 &:= \ip< \scopnkia, \: \scopnkia >_{\scopa} = \pi \: \normgenjac^{(a, 2k)}. \label{eqn:sc:normscop}
}
A method for obtaining explicit recurrence coefficients and evaluating integrals for the weight function $\genjacw^{(a,b)}(x)$ was established in \bsrefchapter{CHAPTER:diskslice} (see also \cite{snowball2019sparse}). The weight is in fact semi-classical, and is equivalent to a generalized Jacobi weight \cite[\S5]{magnus1995painleve}.

@@

\begin{lemma}\label{lemma:sc:Qrecurrence} 
Define
\bseqnnumber{
	\eta_{k} :=
		\begin{cases}
			0 &\text{if } k < 0 \\
			\ch_0 &\text{if } k = 0 \\
			\half &\text{otherwise}
		\end{cases}
}
$\scopnkia(x,y,z)$ satisfy the following recurrences:
\bseqn{
	x \: \scopnkia(x,y,z) &= \alphaa_{n,k,1} \:  \scopa_{n-1, k-1, i}(x, y, z) + \alphaa_{n,k,2} \:  \scopa_{n-1, k+1, i}(x, y, z) \nonumber \\
		& \quad + \alphaa_{n,k,3} \:  \scopa_{n, k-1, i}(x, y, z) + \alphaa_{n,k,4} \:  \scopa_{n, k+1, i}(x, y, z) \nonumber \\
		& \quad + \alphaa_{n,k,5} \:  \scopa_{n+1, k-1, i}(x, y, z) + \alphaa_{n,k,6} \:  \scopa_{n+1, k+1, i}(x, y, z), \\ \\
	y \: \scopnkia(x,y,z) &= \betaa_{n,k,i,1} \:  \scopa_{n-1, k-1, |i-1|}(x, y, z) + \betaa_{n,k,i,2} \:  \scopa_{n-1, k+1, |i-1|}(x, y, z) \nonumber \\
		& \quad + \betaa_{n,k,i,3} \:  \scopa_{n, k-1, |i-1|}(x, y, z) + \betaa_{n,k,i,4} \:  \scopa_{n, k+1, |i-1|}(x, y, z) \nonumber \\
		& \quad + \betaa_{n,k,i,5} \:  \scopa_{n+1, k-1, |i-1|}(x, y, z) + \betaa_{n,k,i,6} \:  \scopa_{n+1, k+1, |i-1|}(x, y, z), \\ \\
	z \: \scopnkia(x,y,z) &= \gammaa_{n,k,1} \: \scopa_{n-1, k, i}(x, y, z) + \gammaa_{n,k,2} \: \scopa_{n, k, i}(x, y, z) \nonumber \\
		& \quad + \gammaa_{n,k,3} \: \scopa_{n+1, k, i}(x, y, z),
}
for $(x,y,z) \in \Omega$, where
\bseqn{
	\alphaa_{n,k,1} &:= \eta_{k-1} \: \ip<\genjacnmk^{(a, 2k)}, \: \genjacnmk^{(a, 2(k-1))}>_{\genjacw^{(a, 2k)}}, \\
	\alphaa_{n,k,2} &:= \eta_{k} \: \ip<\genjacnmk^{(a, 2k)}, \genjac_{n-k-2}^{(a, 2(k+1))}>_{\genjacw^{(a, 2(k+1))}}, \\
	\alphaa_{n,k,3} &:=\eta_{k-1} \: \ip<\genjacnmk^{(a, 2k)}, \: \genjac_{n-k+1}^{(a, 2(k-1))}>_{\genjacw^{(a, 2k)}}, \\
	\alphaa_{n,k,4} &:= \eta_{k} \: \ip<\genjacnmk^{(a, 2k)}, \genjac_{n-k-1}^{(a, 2(k+1))}>_{\genjacw^{(a, 2(k+1))}}, \\
	\alphaa_{n,k,5} &:= \eta_{k-1} \: \ip<\genjacnmk^{(a, 2k)}, \: \genjac_{n-k+2}^{(a, 2(k-1))}>_{\genjacw^{(a, 2k)}}, \\
	\alphaa_{n,k,6} &:=\eta_{k} \: \ip<\genjacnmk^{(a, 2k)}, \genjacnmk^{(a, 2(k+1))}>_{\genjacw^{(a, 2(k+1))}},
}
\bseqn{
	\betaa_{n,k,i,j} &:= 
		\begin{cases}
			- \alphaa_{n,k,j} \quad &\text{if }(i = 0 \text{ and } j \text{ is odd}) \text{ or }(i = 1 \text{ and } j \text{ is even}) \\
			\alphaa_{n,k,j} \quad &\text{otherwise}
		\end{cases}, \\	
	\gammaa_{n,k,1} &:= \beta_{n-k-1}^{(a, 2k)}, \qquad \gammaa_{n,k,2} := \alpha_{n-k}^{(a, 2k)}, \qquad \gammaa_{n,k,3} := \beta_{n-k}^{(a, 2k)}.
}
\end{lemma}

@@

\begin{proof}
	The 3-term recurrence for multiplication by $z$ follows from \bsrefeqn{eqn:sc:Rrecurrence}. For the recurrence for multiplication by $x$, since $\{\scopmjha\}$ for $m = 0,\dots,n+1$, $j = 0,\dots,m$, $h = 0,1$ is an orthogonal basis for any degree $n+1$ polynomial on $\Omega$, we can expand 
\bseqn{
	x \: \scopnkia(x,y,z) = \sum_{m=0}^{n+1} \sum_{j=0}^m \sum_{h=0}^1 c_{m,j} \: \scopmjha(x,y,z).
}
These coefficients are given by
\bseqn{
	c_{m,j} = {\ip< x \: \scopnkia, \scopmjha >_{\scopa}}{\norm{\scopmjha}^{-2}_{\scopa}}
}
where we show the non-zero coefficients that result are the $\alphaa_{n,k,1},\dots,\alphaa_{n,k,6}$ in the lemma.
Recall from \bsrefeqn{eqn:sc:normscop} that $\norm{\scopmjha}_{\scopa}^2 = \pi \: \normgenjac^{(a,2j)}$. Using a change of variables 
\bseqn{
	(\cos\theta \sin\varphi, \: \sin\theta\sin\varphi, \: \cos\varphi) = (x, y, z)
}
we have that, for $m = 0,\dots,n+1$, $j = 0,\dots,m$, 
\bseqn{
	&\ip<x \: \scopnkia, \scopmjha>_{\scopa} \\
	&= \int_\Omega \scopnkia(\xvec,z) \: \scopmjha(\xvec,z) \: x \: \genjacw^{(a,0)}(z) \: \D A \\
	&= \Big( \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \rho(z)^{k+j+1} \: \genjacw^{(a, 0)}(z) \: \D z \Big) \\
	&\quadfour \cdot \Big( \int_0^{2\pi} \chki(\theta) \: \chjh(\theta) \: \cos\theta \: \D \theta \Big) \\
	&= \Big( \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \genjacw^{(a, k + j + 1)}(z) \: \D z \Big) \cdot \: \Big( \int_0^{2\pi} \chki(\theta) \: \chjh(\theta) \: \cos\theta \: \D \theta \Big) \\
	&= \half \: \pi \: \delta_{i,h} \: (\eta_{k-1} \: \delta_{k-1, j} + \eta_{k} \: \delta_{k+1, j})  \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \genjacw^{(a, k + j + 1)}(z) \: \D z
}
where $\delta_{k, j}$ is the standard Kronecker delta function, using \bsreflemma{lemma:sc:Yrecurrence}. Similarly, for the recurrence for multiplication by $y$, we can expand 
\bseqn{
	y \: \scopnkia(x,y,z) = \sum_{m=0}^{n+1} \sum_{j=0}^m \sum_{h=0}^1 d_{m,j} \: \scopmjha(x,y,z).
}
These coefficients are given by
\bseqn{
	d_{m,j} = {\ip< y \: \scopnkia, \scopmjha >_{\scopa}}{\norm{\scopmjha}^{-2}_{\scopa}}
}
where we show the non-zero coefficients that result are the $\betaa_{n,k,1},\dots,\betaa_{n,k,6}$ as stated in the Lemma:
\bseqn{
	&\ip<y \: \scopnkia, \scopmjha>_{\scopa} \\
	&= \int_\Omega \scopnkia(\xvec,z) \: \scopmjha(\xvec,z) \: y \: \genjacw^{(a,0)}(z) \: \D A \\
	&= \Big( \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \rho(z)^{k+j+1} \: \genjacw^{(a, 0)}(z) \: \D z \Big) \\
	&\quadfour \cdot \Big( \int_0^{2\pi} \chki(\theta) \: \chjh(\theta) \: \sin\theta \: \D \theta \Big) \\
	&= \Big( \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \genjacw^{(a, k + j + 1)}(z) \: \D z \Big) \cdot \: \Big( \int_0^{2\pi} \chki(\theta) \: \chjh(\theta) \: \sin\theta \: \D \theta \Big) \\
	&= \half \: \pi \: \delta_{|i-1|,h} \: \big[(-1)^{i+1} \: \eta_{k-1} \: \delta_{k-1, j} + (-1)^i \: \eta_{k} \: \delta_{k+1, j}\big] \\
	&\quadfour \cdot \Big( \int^1_\alpha \genjacnmk^{(a, 2k)}(z) \: \genjacmmj^{(a, 2j)}(z) \: \genjacw^{(a, k + j + 1)}(z) \: \D z \Big)
}
where again $\delta_{k, j}$ is the standard Kronecker delta function, and we have used \bsreflemma{lemma:sc:Yrecurrence}.

@@

For the operator $\calL_W^{(a)\to(a-\tilde a)}$ for the surface Laplacian on a weighted space, the entries of the operator are given by the coefficients in the expansion 
\bseqn{
	\DeltaS \big(\genjacw^{(a,0)} \: \scopnki^{(a)} \big) = \sum_{m=0}^{n} \sum_{j=0}^m \sum_{h=0}^1 c_{m,j,h} \: \genjacw^{(a-\tilde a,0)} \: \scopmjh^{(a - \tilde a)}, 
}	
where the coefficients are
\bseqn{
	c_{m,j,h} = \norm{\scopmjh^{(a - \tilde a)}}^{-2}_{\scop^{(a - \tilde a)}} \ip<\DeltaS \big(\genjacw^{(a,0)} \: \scopnki^{(a)} \big), \: \scopmjh^{(a - \tilde a)}>_{\scop^{(0)}}.
}
Using \bsrefeqn{eqn:sc:woplaplacian}, and integrating by parts thrice, we then have that
\bseqn{
	&\ip<\DeltaS \big(\genjacw^{(a,0)} \: \scopnki^{(a)} \big), \: \scopmjh^{(a - \tilde a)}>_{\scop^{(0)}} \\
	&= \Big( \int_0^{2\pi} \: \chki(\theta) \: \chjh(\theta) \: \D \theta \Big) \\
	&\quadfour \cdot \: \Big( \int_\alpha^1 \Big\{\genjacnmk^{(a,2k)} [-k(k+1) \genjacw^{(2,0)} - 2a(k+1)z \: \genjacw^{(1,0)} + a (a-1) \rho^2] \\
	&\quadeight + \genjacnmk^{(a,2k) \: \prime} [-2(k+1) z \: \genjacw^{(2,0)} + 2a \genjacw^{(1,2)}] \\
	&\quadeight + \genjacnmk^{(a,2k) \: \prime \prime} \: \genjacw^{(2,2)} \Big\} \: \genjacmmj^{(a - \tilde a, 2j)} \: \genjacw^{(a - 2, k+j)} \:  \D z \Big) \\
	&= \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \Big\{ \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacnmk^{(a,2k)} \: \genjacw^{(a - 2, 2k)} \: \big[ -k(k+1) \genjacw^{(2,0)} - 2a(k+1)z \: \genjacw^{(1,0)} \\
	&\quadeight \quadeight \quadtwo \quad + a (a-1) \rho^2 \big] \\
	&\quadeight + a \: \genjacnmk^{(a,2k) \: \prime} \: \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacw^{(a - 1, 2k+2)} \\
	&\quadeight + \genjac_{m-k}^{(a - \tilde a, 2k)} \: \ddx{z} [\genjacnmk^{(a,2k) \: \prime} \: \genjacw^{(a, 2k+2)}] \Big\} \: \D z \\
	&= \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \Big\{ \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacnmk^{(a,2k)} \: \genjacw^{(a - 2, 2k)} \: \big[ -k(k+1) \genjacw^{(2,0)} - 2a(k+1)z \: \genjacw^{(1,0)} \\
	&\quadeight \quadeight \quadtwo \quad + a (a-1) \rho^2 \big] \\
	&\quadeight + a \: \genjacnmk^{(a,2k) \: \prime} \: \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacw^{(a - 1, 2k+2)} \\
	&\quadeight + \genjacnmk^{(a,2k)} \: \genjacw^{(a-1, 2k)} \big[ \genjac_{m-k}^{(a - \tilde a, 2k) \: \prime \prime} \: \genjacw^{(1, 2)} + a \genjac_{m-k}^{(a - \tilde a, 2k) \: \prime} \: \rho^2 \\
	&\quadeight \quadeight \quadtwo \quad - 2(k+1) z \: \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacw^{(1, 0)} \big] \Big\} \: \D z
}
\bseqn{
	&= \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \Big\{ \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacnmk^{(a,2k)} \: \genjacw^{(a - 2, 2k)} \: \big[ -k(k+1) \genjacw^{(2,0)} - 2a(k+1)z \: \genjacw^{(1,0)} \\
	&\quadeight \quadeight \quadtwo \quad + a (a-1) \rho^2 \big] \\
	&\quadfour \quadtwo + \genjacnmk^{(a,2k)} \: \genjacw^{(a - 1, 2k+2)} \big[ \genjac_{m-k}^{(a - \tilde a, 2k) \: \prime \prime} \: \rho^2 - 2(k+1) z \: \genjac_{m-k}^{(a - \tilde a, 2k) \: \prime} \big] \\
	&\quadfour \quadtwo - a \genjacnmk^{(a,2k)} \: \genjac_{m-k}^{(a - \tilde a, 2k)} \: \genjacw^{(a-2, 2k)} \: \big[ (a-1) \rho^2 - 2(k+1) z \: \genjacw^{(1, 0)} \big] \Big\} \: \D z \\
	&= \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \genjacnmk^{(a,2k)} \: \genjacw^{(a, 2k)} \: r_{m-k} \: \D z
}
where $r_{m-k}$ is a degree $m - k$ polynomial in $z$, and so the above is zero for $n - k > m - k \iff m < n$.
